Lessons learned from bugs in models of human history

### 2020-05-21 paper.tex
Remove a few comments
affiliations

\title{Lessons learned from bugs in models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill University and Genome Qu\'{e}bec Innovation Centre,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

%\aprcomment{title thoughts: \\
%Reducing errors in demographic model design and implementation \\
%Lessons learned from misspecified models of human history \\
%Lessons learned from buggy models of human history \\
%Lessons learned from bugs in population genetics models
%}

\sgcomment{How to avoid simulating the wrong demographic model}

>>>>

\title{Lessons learned from bugs in models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill Genome Centre and Department of Human Genetics,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle
